---
name: "Maja and Fabian"
title: "Fighting Twitterbots"
description: |
  Finding and evaluating twitter bots in a #Drosten related dataset
output: 
postcards:: jolla
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```


## Why is this important? 

Detecting non-human Twitter users has been of interest to academics. Indiana University has developed a free service called **Botometer**, which scores Twitter handles based on their likelihood of being a Twitterbot. Already in 2009, Twitter bots were estimated to create approximately 24% of tweets on Twitter. One academic study in 2017 estimated that **up to 15%** of Twitter users were automated bot accounts. And the prevalence of Twitter bots coupled with the ability of some bots to give seemingly human responses has enabled these non-human accounts to garner **widespread influence**, in both positive and negative ways. 

This project will address the question whether a **specific twitter dataset** - consisting of all tweets mentioning #Drosten or @c_drosten in the years 2020 and 2021 - contains bots and how they evolve over time. 


## Research Questions

1. Which percentage of the total number of tweets originate from bots and does this change as the pandemic progresses?  

2. Are bots and non-bots taking talking in a different valence?

## The data

```{r}
#load(xx)

#head(xx)
```


## Methods

**Botometer**

1. Step [x] Process all tweets by using the botometer API: https://botometer.osome.iu.edu

2. Step [ ] Interpret the results and find a suited threshold 

3. Step [ ] Analyse the results: Frequency and distribution over time 

**Sentiment Analysis**

4. Step [ ] Perform Sentiment Analysis with the tweets indenified as "bot-like"



## Implications

This small project attempts to contribute to the detection of possible bots in a Twitter dataset related to tweets mentioning Christian Drosten using #drosten or @c_drosten. It can provide us with information about the **extent to which these Twitter hashtags have been used by bots**. 

In addition, the value of bot tweets can tell us more about the origin and goals of the bots created and provide an answer to the question of **whether bots were pushing certain issues**.   
 



